Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-15 article.qmd
Add authors

    We believe that this Python-centric approach positions Poincaré and SimBio as valuable tools for the modeling community.
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
---

>>>>

    We believe that this Python-centric approach positions Poincaré and SimBio as valuable tools for the modeling community.

authors:
    -   name: Mauro Silberberg
        orcid: 0000-0002-2402-1100
        email: maurosilber@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET
    -   name: Rahuman S. Malik-Sheriff
        orcid: 0000-0003-0705-9809
        email: sheriff@ebi.ac.uk
        affiliations:
        -   ref: EBI
    -   name: Hernán E. Grecco
        corresponding: true
        orcid: 0000-0002-1165-4320
        email: hgrecco@df.uba.ar
        affiliations:
        -   ref: UBA
        -   ref: CONICET

affiliations:
    -   id: UBA
        name: Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Física. Buenos Aires, Argentina.
    -   id: CONICET
        name: CONICET - Universidad de Buenos Aires, Instituto de Física de Buenos Aires (IFIBA). Buenos Aires, Argentina
    -   id: EBI
        name: European Bioinformatics Institute, European Molecular Biology Laboratory (EMBL-EBI), Wellcome Trust Genome Campus, Cambridge, UK
        url: https://ebi.ac.uk/

bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
---
